---
title: "Check and Tabulate File Headers"
author: "Dan Johnson"
date: "6/1/2021"
output: html_document
---
# Goals
This script creates a CSV table using the headers from TXT versions of the lab reports as input. It serves two functions:

* The table makes it easy to check that the files have been fully de-identified.
* The table serves as a data frame of the headers on files in a folder that can be assembled into a larger file for analysis.

The current script is not set to recursively read sub-folders, but can be modified to do so.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set the libraries.
```{r libraries}
library(magrittr)
library(tidyverse)
library(readtext)
library(stringr)
library(tidyr)
# library(readr)
# library(tm)
# library(quanteda)
```

```{r create files list}
# This creates a list of files in the current directory folder
#
filelist <- list.files()

# Alternative is: folder_file_names <- list.files(pattern="*.txt")
```


```{r make_df}
# This sets variables and creates a data frame of .txt files from the folder, using the 'path' 
path <- getwd()
filelist <- list.files()
extracted_texts <- readtext(filelist)
# Produces a 2-column table of doc_id and text
```


```{r split_df}
# This takes the full document in the two-column table and parses the lines
# using the newline "\n" to identify the line breaks.
# This version only keeps the selected rows of the header, and throws away all other text.
#
tabled_texts <- extracted_texts %>% separate(text,c("row1","row2","row3","row4","row5","row6","row7","row8","row9"),"\n")
View(tabled_texts)
write_csv(tabled_texts, "collated_texts.csv", na = "NA", append = FALSE, col_names = TRUE, quote_escape = "double", eol = "\n")
```


